Supplementary material: The increasing cost of happiness

### 2021-01-12 src/supplementary.Rmd
Added population weights and residual plots

##### Figure S3. Cubic spline of household wealth on satisfaction and happiness
```{r losat_gh9_hwnwip}
source("../src/happyfun.r")
happywealth <- read_rds("../data/happywealth.rds")

@@

There were _df_ = 59,876 total observations. 4000 samples (post-warmup) were drawn using sampling(NUTS). For each parameter, Bulk_ESS and Tail_ESS are effective sample size measures, and Rhat is the potential scale reduction factor on split chains (at convergence, Rhat = 1).

@@

##### Figure S5. Posterior predictive distribution of marginal effect of wealth by year (95% CI)  
(not run)

```{r figure_s2, fig.height = 3, eval=F}
library(brms)

marginals <- conditional_effects(
  hifdip_gh9_fixed_fit,
  effects = c("dollars:year"), # year, dollars, 
  method = "fitted"
  )

marginals$`dollars:year`$year <- factor(marginals$`dollars:year`$year, 
                                        levels = c("2002", "2006", "2010", "2014", "2018"))

plot(marginals, plot=F)[[1]] +
  xlim(c(0, 30)) +
  ylim(c(-0.5, 1)) +
  facet_wrap(~year, nrow=1) +
  theme_test() +
  theme(legend.position = "none") +
  labs(x = "", y = "")
```

>>>>

@@

There were _df_ = 59,876 total observations. 4000 samples (post-warmup) were drawn using sampling(NUTS). For each parameter, Bulk_ESS and Tail_ESS are effective sample size (ESS) measures, and Rhat is the potential scale reduction factor on split chains. In each case the Rhat apprached 1, indicating convergance. The smallest ESS was _n_ = 472, which is greater than a conservative estimate of the sufficient _n_ for estimation (*n* > 300).

@@

##### Figure S3. Residual plots for piecewise happiness models
```{r figure_s3, fig.height=9, fig.width=9}
# https://www.flutterbys.com.au/stats/tut/tut7.2b.html
# resid = resid(data.brms)[, "Estimate"]
# fit = fitted(data.brms)[, "Estimate"]

resid_df <- readRDS("../results/residual_data.RDS")

resid_df %>%
  group_by(year) %>%
  slice_sample(n = 1000) %>% # to reduce overplotting
  ggplot(aes(x = fitteds, y = resids)) +
    geom_point(alpha = 0.1, size = 0.5) +
    facet_wrap(~year, scales = "free") +
    theme_test()
```

```
Figure S3 legend: The joint distribution between residual and fitted values shows no common patterns across years and appears clustered around zero in each case.
```

Examination of the residual plots from the piecewise models of happiness confirms the residuals were evenly distributed around zero and there was little indication of heterscedascity. There was little evidence that the piecewise models of happiness were not appropriate for the data.

##### Figure S4. Cubic spline of household wealth on satisfaction and happiness
```{r losat_gh9_hwnwip}
source("../src/happyfun.r")
happywealth <- read_rds("../data/happywealth.rds")

##### Figure S5. Prior predictive plot
(Not included)

```{r figure_s5, eval=F}
# prior_fit <- readRDS("../results/prior_nl_hifdip_losat_cov_2018.RDS")

# Check priors. The fixed estimates should be near zero, the fixed error should
# be ~3 respectively
# 
# summary(prior_fit)

# Extract prior predictions
# d <- data.frame(predict(prior_fit)) # takes a long time to run
# prior_predictions <- bind_cols(prior_fit$data, d)
# write_rds(prior_predictions, "../results/prior_prediction_data.RDS")

prior_predictions <- read_rds("../results/prior_prediction_data.RDS")

prior_predictions %>%
  mutate(
      dollar_bin = ntile(dollars, 10)
      ) %>%
    group_by(dollar_bin) %>%
    summarize(
      wellbeing = mean(Estimate, na.rm=T),
      wealth = mean(dollars, na.rm=T),
      n = n()
    ) -> df.deciles

prior_predictions %>%
  rename(wellbeing = Estimate,
         wealth = dollars) -> df.plot

# piecewise model
p0 <- ggplot(df.deciles, aes(x = wealth, y = wellbeing)) +
  geom_point() +
  geom_smooth(data = df.plot,
              aes(x = wealth, y = wellbeing,
                  fill = "#C79999", color = "#8F2727"),
              size = 0.5) +
  coord_cartesian(xlim = c(0, max(df.deciles$wealth)),
                  ylim = c(min(df.deciles$wellbeing), max(df.deciles$wellbeing))
                  ) +
  theme_test() +
  theme(legend.position = "none")

p1 <- ggplot(df.deciles, aes(x = wealth, y = wellbeing)) +
  geom_point() +
  geom_smooth(data = df.plot,
              aes(x = wealth, y = wellbeing, fill = "manual"),
              method = "lm",
              size = 0.5) +
  coord_cartesian(xlim = c(0, max(df.deciles$wealth)),
                  ylim = c(min(df.deciles$wellbeing), max(df.deciles$wellbeing))
                  ) +
  theme_test() +
  theme(legend.position = "none") +
  scale_fill_manual(values = "#b3cde0")

source("happyfun.R")

p2 <- prior_predictions %>%
  rownames_to_column(var = "xwaveid") %>%
  mutate(year = 2018,
         dollars = dollars*10000) %>%
  rename(Wellbeing = Estimate, `Household income` = dollars) %>% 
  plot_inflection_piecewise(Wellbeing, `Household income`, knots = 1)

p3 <- prior_predictions %>%
  rownames_to_column(var = "xwaveid") %>%
  mutate(year = 2018,
         dollars = dollars*10000) %>%
  rename(Wellbeing = Estimate, `Household income` = dollars) %>% 
  plot_inflection_cubic(Wellbeing, `Household income`)

p4 <- prior_predictions %>%
  rownames_to_column(var = "xwaveid") %>%
  mutate(year = 2018,
         dollars = dollars*10000) %>%
  rename(Wellbeing = Estimate, `Household income` = dollars) %>% 
  plot_linear(Wellbeing, `Household income`) +
  scale_fill_manual(values = "#b3cde0") +
  scale_color_manual(values = "#005b96")

p0 + p1

p2 + p3 + p4
```

<br><br><br>

##### Figure S6. Marginal effect of wealth on satisfaction by year (95% CI)  
(Not included)
```{r figure_s6_df, eval=F}
# Do not run

library(brms)

# import the fits
nl_losat_paths <- list.files(
  path = "../results/no_topcodes/",
  pattern = "fit_nl_hifdip_losat_cov_*",
  full.names = TRUE
)

list_fits = list()
for (f in nl_losat_paths) {
  fit <- readRDS(f)
  list_fits[str_extract(f, "[[:digit:]]+")] <- list(fit)
}

# turn each fit into a plot dataframe (this takes a few minutes)
plot_data <- map_dfr(.x = list_fits, 
                     .f = function(x) conditional_effects(x)[[1]],
                     .id = "Year")

saveRDS(plot_data, "../results/nl_marginal_effects_losat.RDS")
```
```{r, figure_s6, eval=F}
readRDS("../results/nl_marginal_effects_losat.RDS") %>%
  ggplot(aes(x = dollars, y = estimate__, fill = Year)) +
    geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.25) +
    geom_line(aes(color = Year)) +
    facet_wrap(~Year, scale = "free") +
    labs(y = "") +
    theme_test() +
    theme(legend.position = "none")
```
